\section{Bibliografía}
\label{sec:biblio}

\begin{thebibliography}{9}
\bibitem{engel2012}
    J. Engel, J. Sturm, and D. Cremers,
    \textit{''Camera-based navigation of a low-cost quadrocopter''}.
    Conference on Intelligent Robots and Systems (IROS),
    2012.
    
\bibitem{engel2014}
    J. Engel, J. Sturm, and D. Cremers,
    ''\textit{Scale-aware navigation of a low-cost quadrocopter with a monocular camera''}.
    Robotics and Autonomous Systems, 
    2014.

\bibitem{hausman2016}
    K. Hausman, S. Weiss, R. Brockers, L. Matthies, and G.S. Sukhatme,
    \textit{''Self-calibrating multi-sensor fusion with probabilistic measurement validation for seamless sensor switching on a UAV''}.
    IEEE International Conference on Robotics and Automation (ICRA),
    2016.

\bibitem{qi2009}
    J. Qi, D. Song, L. Dai and J. Han,
    ''\textit{Design, Implement and Testing of a Rotorcraft UAV System''}.
    Aerial Vehicles, 
    January 2009.

\bibitem{delrosario2016}
    Del Rosario M, Lovell N, Redmond S,
    \textit{''Quaternion-based Complementary Filter for Attitude Determination of a Smartphone''}.
    IEEE Sensors Journal,
    Jun 2016.

\bibitem{caron2006}
    Caron F, Duflos E, Pomorski D, Vanheeghe P,
    \textit{''GPS/IMU data fusion using multisensor Kalman filtering: introduction of contextual aspects''}.
    Information Fusion,
    2006 Jun 30,
    7(2):221-30.
    
\bibitem{mirzaei2008}
    Mirzaei FM, Roumeliotis S,
    \textit{''A Kalman filter-based algorithm for IMU-camera calibration: Observability analysis and performance evaluation''}.
    Robotics, IEEE Transactions,
    2008 Oct,
    24(5):1143-56.

\bibitem{hesch2009}
    Hesch J, Mirzaei FM, Mariottini GL, Roumeliotis S,
    \textit{''A 3d pose estimator for the visually impaired''}.
    IEEE/RSJ International Conference,
    2009 Oct 10,
    (pp. 2716-2723),
    IEEE.
    
\bibitem{chambers2014}
    Chambers A, Scherer S, Yoder L, Jain S, Nuske S, Singh S,
    \textit{''Robust multi-sensor fusion for micro aerial vehicle navigation in GPS-degraded/denied environments''}.
    InAmerican Control Conference (ACC),
    2014 Jun 4, 
    pp. 1892-1899, IEEE.

\bibitem{hesch2013}
    Hesch JA, Kottas DG, Bowman SL, Roumeliotis SI,
    \textit{''Camera-IMU-based localization: Observability analysis and consistency improvement''}.
    The International Journal of Robotics Research,
    2013.

\bibitem{lee2016}
    S. Lee, D. Har, and D. Kum,
    \textit{''Drone-Assisted Disaster Management: Finding Victims via Infrared Camera and Lidar Sensor Fusion''}.
    3rd Asia-Pacific World Congress on Computer Science and Engineering, 
    2016.

\bibitem{shah2017}
    M. Shah, R. Kapdi,
    \textit{''Object detection using deep neural networks''}.
     International Conference on Intelligent Computing and Control Systems (ICICCS),
     2017.
     
\bibitem{autopilot}
    Aautopilot Project,
    \url{https://autopilot-project.eu/}.
    Última vez accedido el 03-08-2018.

\bibitem{pc104}
    PC/104 Embedded Consortium,
    \textit{''PC/104 Specification''}.
    Version 2.6,
    October 13, 2008.

\bibitem{pci104express}
    PC/104 Consortium,
    \textit{''PCI/104-Express \& PCIe/104 Specification''}.
    Version 3.0,
    February 17, 2015
    
\bibitem{endres2012}
    F. Endres, J. Hess, N. Engelhard,
    \textit{''An Evaluation of the RGB-D SLAM System''}.
    2012 IEEE International Conference on Robotics and Automation,
    2012
    
\bibitem{davison2007}
    A. Davison, I. Reid, O. Stasse
    \textit{''MonoSLAM: Real-Time Single Camera SLAM''},
    IEEE Trans. On Pattern Analysis And Machine Intelligence,
    2007
    
\bibitem{botterill2013}
    T. Botterill, S. Mills, R. Green,
    \textit{''Collecting Scale Drift by Object Recognition in Single-Camera SLAM''},
    IEEE Trans. Cybernetics, vol. 43, no.6, pp. 1767-1780,
    2013

\bibitem{sola2007}
    J. Solà,
    \textit{''Towards Visual Localization, Mapping and Moving Objects Tracking by a Mobile Robot: A Geometric and Probabilistic Approach},
    LAAS, Tolouse,
    2007
    
\bibitem{murray2007}
    G. Klein, D. Murray,
    \textit{''Parallel tracking and mapping for small AR workspaces''},
    Proc. Sixth IEEE and ACM International Symposium on Mixed and augmented Reality,
    2007
    
\bibitem{trivedi2013}
    P. Trivedi, T. Agarwal, K. Muthunagai,
    \textit{''MC-RANSAC: A Pre-processing Model for RANSAC using Monte Carlo method implemented on a GPU''}
    2013 International Conference on Advances in Computing, Communications and Informatics (ICACCI),
    2013
    
\bibitem{kaehler2017}
    A. Kaehler, G. Bradski,
    \textit{''Learning OpenCV3: Computer vision in C++ with the OpenCV library''},
    O'Reilly Media, Inc.,
    2017
    
\bibitem{carlson2010}
    J. Carlson
    \textit{''Mapping Large, Urban Environments with GPS-Aided SLAM''},
    The Robotics Institute, Carnegie Mellon University Pittsburgh, Pennsylvania,
    2010
    
\bibitem{weinmann2016}
    M. Weinmann,
    \textit{''Reconstruction and Analysis of 3D Scenes''},
    Institute of Photogrammetry and Remote Sensing Karlsruhe Institute of Technology Karlsruhe Germany,
    2016
    
\bibitem{garcia2017}
    F. Garcia,
    \textit{''Tools for 3D Point Cloud Registration''},
    Doctoral Program in Technology, Girona,
    2017
    
\bibitem{barazzetti2018}
    L. Barazzetti,
    \textit{''Point cloud occlusion recovery with shallow feedforward neural networks''},
    Advanced Engineering Informatics,
    2018
    
\bibitem{besl1992}
    P. Besl, N. McKay,
    \textit{''A method for registration of 3-D shapes''},
    IEEE Transactions on Pattern Analysis and Machine Intelligence (PAMI), vol. 14, no. 2, pp. 239– 256, 
    1992.
    
\bibitem{chen1992}
    Y. Chen, G. Medioni,
    \textit{''Object modelling by registra- tion of multiple range images''},
    Image Vision Comput., vol. 10, no. 3, pp. 145–155,
    1992
    
\bibitem{rusinkiewicz2001}
    S. Rusinkiewicz, M. Levoy,
    \textit{''Efficient variants of the ICP algorithm''},
    Proceedings Third International Conference on 3-D Digital Imaging and Modeling,
    2001
    
\bibitem{harris1988}
    C. Harris, M. Stephens,
    \textit{''A combined corner and edge detection''},
    4th Alvey Vision Conference, pp. 147-151,
    1988
    
\bibitem{schmid2000}
    C. Schmid, R. Mohr, C. Bauckhage,
    \textit{''Evaluation of interest point detectors''},
    Int. J. Comput. Vis. 37(2), 151–172,
    2000
    
\bibitem{sipiran2011}
    I. Sipiran, B. Bustos,
    \textit{''Harris 3D: A robust extension of the Harris operator for interest point detection on 3D meshes''},
    The Visual Computer,
    2011
    
\bibitem{jollife2016}
    I. Jollife, J. Cadima,
    \textit{''Principal component analysis: A review and recent developments''},
    Philosophical Transactions of the Royal Society A: Mathematical, Physical and Engineering Sciences,
    2016
    
\bibitem{fischler1981}
    M. Fischler, R. Bolles,
    \textit{''Random sample consensus: a paradigm for model fitting with applications to image analysis and automated cartography''},
    Commun. ACM, vol. 24, no. 6, pp. 381–395,
    1981.
    
\bibitem{horn1987}
    B. Horn,
    \textit{''Closed-form solution of absolute ori- entation using unit quaternions''}
    Journal of the Optical Society of America A, vol. 4, no. 4, pp. 629–642,
    1987.
    
\bibitem{arun1987}
    K. Arun, T. Huang, S. Blostein,
    \textit{''Least- squares fitting of two 3-D point sets''},
    IEEE Transactions on Pattern Analysis and Machine Intelligence (PAMI), vol. 9, no. 5, pp. 698–700,
    1987.
    
\bibitem{eggert1997}
    D. Eggert, A. Lorusso, R. Fischer,
    \textit{''Estimating 3-D rigid body transformations: a comparison of four major algorithms''},
    Mach. Vision Appl., vol. 9, no. 5-6, pp. 272–290,
    1997.
    
\bibitem{fitzgibbon2001}
    A. Fitzgibbon,
    \textit{''Robust registration of 2D and 3D point sets''},
    British Machine Vision Conference (BMVC), pp. 411–420,
    2001.
    
\bibitem{low2004}
    K. Low,
    \textit{''Linear least-squares optimization for point- to-plane ICP surface registration''},
    Technical Report TR04-004, Department of Computer Science, University of North Carolina at Chapel Hill,
    2004.
    
\bibitem{holz2015}
    D. Holz, A. Ichim, F. Tombari, R. Rusu, S. Behnke,
    \textit{''Registration with the point cloud library: A modular framework for aligning in 3-D''},
    IEEE Robotics and Automation Magazine,
    2015.
    
\bibitem{holzer2012}
    S. Holzer, R. Rusu, M. Dixon, S. Gedikli, N. Navab,
    \textit{''Real-Time Surface Normal Estimation from Organized Point Cloud Data Using Integral Images''},
    IEEE/RSJInternational Conference on IntelligentRobots and Systems (IROS), Vila Moura, Algarve, Portugal,
    2012.

\bibitem{nguyen2012}
    C. Nguyen, S. Izadi, D. Lovell,
    \textit{''Modeling kinect sensor noise for improved 3d reconstruction and tracking''},
    3D Imaging, Modeling, Processing, Visualiza- tion andTransmission (3DIMPVT), Second International Conference on, pp. 524 –530,
    2012
\end{thebibliography}

